idealista18: A data package with real estate information in three major Spanish markets from the Idealista database

### 2021-11-05 data-in-brief/dib-idealista18.tex
Updated edits to dib-idealista.tex
Started editing Data in Brief paper

The data sets is composed by three items for three major spanish cities: quarterly single family listings, neighboorhood polygons and a set key of Points of Interest for each city. All spatial features, such as polygons and points, are expressed in geodetic coordinates using the \emph{EPSG:4326} coordinate reference system. The first block of data integrates properties published on idealista web site \cite{idealista}; each file contains the complete offering for a city for the four quarters in 2018. Idealista is the major real estate listing portal in Spain and also present in other southern european countries as Italy and Portugal. Each record contains the key found in listing ad\footnote{we will use the term \emph{ad} or \emph{listing} interchangeably to refer to a house published on the portal} plus a number of additional attribues from the Spanish cadastre \cite{Catastro}. The latter are described in the table \ref{table:data-assets-variables}, and the names for all these variables start with the prefix \emph{CAD}. Cadastral features asssignment is done by assigning the features of the nearest parcel to the coordinates \emph{LATITUDE} and \emph{LONGITUDE}. The measure scales for each variable has been defined according the theoretical framework proposed by \cite{stevens1946theory} that defines four scales: nominal, ordinal, interval and ratio.

>>>>

This data package is composed of data objects corresponding to three major Spanish cities: quarterly single family listings, neighboorhood polygons and a set key of Points of Interest for each city. All spatial features, such as polygons and points, are expressed in geodetic coordinates using the \emph{EPSG:4326} coordinate reference system. The first block of data integrates properties published on idealista web site \cite{idealista}; each file contains the complete offering for a city for the four quarters in 2018. Idealista is the major real estate listing portal in Spain and also present in other southern european countries as Italy and Portugal. Each record contains the key found in listing ad\footnote{we will use the term \emph{ad} or \emph{listing} interchangeably to refer to a house published on the portal} plus a number of additional attribues from the Spanish cadastre \cite{Catastro}. The latter are described in the table \ref{table:data-assets-variables}, and the names for all these variables start with the prefix \emph{CAD}. Cadastral features asssignment is done by assigning the features of the nearest parcel to the coordinates \emph{LATITUDE} and \emph{LONGITUDE}. The measure scales for each variable has been defined according the theoretical framework proposed by \cite{stevens1946theory} that defines four scales: nominal, ordinal, interval and ratio.
